False Positive Probabilities for all Kepler Objects of Interest: \\ \nvalnew\ newly validated planets and \nfpnew\ likely false positives

### 2015-08-31 ms.tex
paper edits

\newcommand{\nreliable}{2752}
\newcommand{\nval}{2069}
\newcommand{\nreliableFP}{292}
\newcommand{\nvalnew}{1396}
\newcommand{\nfpnew}{192}
\newcommand{\ncurval}{1001}

@@

@@

\begin{abstract}
We present the results of applying a fully automated transit signal
false positive probability calculating procedure to every
\kepler\ Object of Interest (KOI).  Out of \ncalc\ KOIs, we determine
that \nval\ have probabilities $<$1\% to be astrophysical false
positives, and thus may be considered validated planets.  \nvalnew\ of
these have not yet been validated or confirmed by other methods.  In
addition, we identify \nfpnew\ KOIs likely to be false positives
($>$90\% \nfpnew) that have not yet been identified as such. A side
product of these calculations is full stellar property posterior
samplings for every host star, modeled as single, binary, and triple
systems.  These calculations use \vespa, a publicly available Python
package able to be easily applied to any transiting exoplanet
candidate.
\end{abstract}

@@

The \vespa\ procedure models an eclipse signal as a simple trapezoid,
parametrized by depth $\delta$, total duration $T$, and shape
parameter $T / \tau$, where $\tau$ is the ``ingress/egress'' duration
(such that a completely V-shaped transit has $T/\tau = 2$).  For the
transit signal being evaluated, the joint posterior probability
density function (PDF) of these shape parameters is sampled with
Markov Chain Monte Carlo (MCMC), using the \texttt{emcee} sampler
\citep{emcee}.  This allows the likelihood for each hypothesis to be
determined by simulating a physically realistic population of the
hypothesized astrophysical scenario and using this population to
define the PDF for the trapezoidal parameters under the hypothesis.
The likelihood is then
\begin{equation}
  \eqlabel{lhood}
  \mathcal L_i = \displaystyle \int p_\mathrm{sig}\left(\bvec{\theta}\right)
                                    p_i\left(\bvec{\theta}\right)\,d\bvec{\theta},
\end{equation}
where $\bvec{\theta}$ is the vector of trapezoidal shape parameters,
$p_\mathrm{sig}$ is the posterior PDF of the signal, and $p_i$ is the
PDF for the parameters under hypothesis $i$.\footnote{$\mathcal L_i$
  may be seen to be the ``evidence'' or ``marginalized likelihood'' of
  the trapezoidal model under hypothesis $i$, with $p_\mathrm{sig}$
  being the likelihood and $p_i$ being the prior, integrated over the
  $\bvec{\theta}$ parameter space.  But for clarity, and for
  continuity with previous publications, we continue to call $\mathcal
  L_i$ the ``likelihood'' for hypothesis $i$.}  The hypotheses
currently supported by \vespa\ are the following: unblended eclipsing
binary (EB), hierarchical-triple eclipsing binary (HEB),
chance-aligned background/foreground eclipsing binary (BEB), and
transiting planet (Pl).

@@

To enable interpretation, \tab{fpp} thus contains both the current KOI
disposition and the results of the positional probability calculations
of \citet{Bryson:2015}.  \Fig{fppall} shows FPPs for all KOIs passing
the following criteria:
\begin{itemize}
\item Dispositioned CANDIDATE or CONFIRMED at the NExScI archive,
\item $> 0.99$ probability to be on the target star, according
  to \citet{Bryson:2015}, along with a positional probability
  ``score'' $> 0.4$ (indicating a reliable result), and   
\item $L_{\rm tot} > 1e-3$, indicating that not all the hypotheses are
  poor fits to the transit signal.
\end{itemize}

@@

@@

In this work, we have calculated the astrophysical false positive
probability (FPP) for every \kepler\ object of interest (KOI), using
the publicly available Python module \vespa.  While the assumptions
behind this calculation are not necessarily valid for every KOI (see
\sect{results:fpp}, we have identified \nvalnew\ KOIs that have
reliable FPPs of $< 0.01$, resulting in validation of their planetary
nature at the 99\% confidence level.  The reliability of these
calculations is dependent largely on the results of \citet{Bryson:2015},
which quantify the probability that the eclipse/transit signal is
spatially coincident on the sky with the presumed target star.

These batch FPP calculations will

@@

\begin{figure*}[p]
\begin{center}
\includegraphics[width=7in]{figures/fpp_summary_all.pdf}
\end{center}
\caption{False positive probabilities of all CANDIDATE or CONFIRMED
  KOIs for which we consider the \vespa\ calculations to be reliable
  (floored at $10^{-4}$ for visualization purposes), meaning they are
  considered to be reliably located on the target star ($ {\rm Pr} >
  0.99$, with ``score'' $>$ 0.4) according to pixel-level analysis
  \citep{Bryson:2015}, and have $L_{\rm tot} > 10^{-3}$, indicating
  that the hypotheses tested by \vespa\ are not all poor explanations
  of the data (see \sect{results:fpp}).  Of these \nreliable\ KOIs,
  \nval\ have FPPs less than 1\% (\nvalnew\ of which have not yet been
  dispositioned as CONFIRMED).  Noteably, \nreliableFP\ are likely
  false positives (FPP $> 0.5$), consistent with the
  \citet{Morton:2011} and \citet{Fressin:2013} \emph{a priori}
  estimates of the overall \kepler\ candidate false positive rate.
  \figlabel{fppall}}
\end{figure*}

\begin{figure*}[p]
\begin{center}
\includegraphics[width=7in]{figures/fpp_pie.pdf}
\end{center}
\caption{A summary of how the the calculations presented in this paper
  advance our understanding of the true nature of KOIs.  More than
  half of all KOIs to date have already been dispositioned FALSE
  POSITIVE or CONFIRMED.  Those dispositioned CANDIDATE we further
  categorize according to their reliability.  The ``no reliable
  calculation'' category means that either the \vespa\ calculation was
  not successful, or that $L_{\rm tot} < 10^{-3}$.  ``On-target
  probability uncertain'' indicates that the positional probability
  calculations of \citet{Bryson:2015} are not reliable (score $<
  0.4$).  ``On-target probability $<$ 0.99'' means that the positional
  probability calculations indicate that there is a non-negligible
  chance that the source of the transit signal is not at the position
  of the KOI.  The remaining three categories are all CANDIDATE KOIs
  reliably confirmed to be located at the presumed target star,
  grouped by false positive probability.  \nvalnew\ of these are new
  planet validations, and \nfpnew\ are new likely false positives.
  \figlabel{fpppie}}
\end{figure*}

>>>>

\newcommand{\nreliable}{2854}
\newcommand{\nval}{2136}
\newcommand{\nreliableFP}{298}
\newcommand{\nvalnew}{1456}
\newcommand{\nfpnew}{195}
\newcommand{\ncurval}{1001}

\newcommand{\posprobthresh}{0.3}

@@

\newcommand{\dataurl}{\url{http://tigress-web.princeton.edu/~tmorton/koi-fpp/}}

@@

\begin{abstract}
We present the results of applying a fully automated transit signal
false positive probability calculating procedure to every
\kepler\ Object of Interest (KOI).  Out of \ncalc\ KOIs, we determine
that \nval\ have probabilities $<$1\% to be astrophysical false
positives, and thus may be considered validated planets.  \nvalnew\ of
these have not yet been validated or confirmed by other methods.  In
addition, we identify \nfpnew\ KOIs likely to be false positives
($>$90\%) that have not yet been identified as such. A side
product of these calculations is full stellar property posterior
samplings for every host star, modeled as single, binary, and triple
systems.  These calculations use \vespa, a publicly available Python
package able to be easily applied to any transiting exoplanet
candidate.
\end{abstract}

@@

The \vespa\ procedure models an eclipse signal as a simple trapezoid,
parametrized by depth $\delta$, total duration $T$, and shape
parameter $T / \tau$, where $\tau$ is the ``ingress/egress'' duration
(such that a completely V-shaped transit has $T/\tau = 2$).  For the
transit signal being evaluated, the joint posterior probability
density function (PDF) of these shape parameters is sampled with
Markov Chain Monte Carlo (MCMC), using the \texttt{emcee} sampler
\citep{emcee}.  This allows the likelihood for each hypothesis to be
determined by simulating a physically realistic population of the
hypothesized astrophysical scenario and using this population to
define the PDF for the trapezoidal parameters under the hypothesis.
The likelihood is then
\begin{equation}
  \eqlabel{lhood}
  \mathcal L_i = \displaystyle \int p_\mathrm{sig}\left(\bvec{\theta}\right)
                                    p_i\left(\bvec{\theta}\right)\,d\bvec{\theta},
\end{equation}
where $\bvec{\theta}$ is the vector of trapezoidal shape parameters,
$p_\mathrm{sig}$ is the posterior PDF of the signal, and $p_i$ is the
PDF for the parameters under hypothesis $i$.\footnote{$\mathcal L_i$
  may be seen to be the ``evidence'' or ``marginalized likelihood'' of
  the trapezoidal model under hypothesis $i$, with $p_\mathrm{sig}$
  being the likelihood and $p_i$ being the prior, integrated over the
  $\bvec{\theta}$ parameter space.  But for clarity, and for
  continuity with previous publications, we continue to call $\mathcal
  L_i$ the ``likelihood'' for hypothesis $i$.}  The hypotheses
currently supported by \vespa\ are the following: unblended eclipsing
binary (EB), hierarchical-triple eclipsing binary (HEB),
chance-aligned background/foreground eclipsing binary (BEB), and
transiting planet (Pl).  We note that the determination of the diluted
eclipse depth of these blended scenarios assumes that the blended
system is \emph{fully contained} within the target's photometric
aperture.  That is, these scenarios do not account for the possibility
that only a small fraction of the light from a nearby contaminating
star might be in the aperture, many of which have already been
identified via other methods \cite{Bryson:2013,Coughlin:2014}.

@@

To enable interpretation, \tab{fpp} thus contains both the current KOI
disposition and the results of the positional probability calculations
of \citet{Bryson:KSCI}.  \Fig{fppall} shows FPPs for all KOIs passing
the following criteria:
\begin{itemize}
\item Dispositioned CANDIDATE or CONFIRMED at the NExScI archive,
\item $> 0.99$ probability to be on the target star, according
  to \citet{Bryson:KSCI}, along with a positional probability
  ``score'' $> \posprobthresh$ (indicating a reliable result), and   
\item $L_{\rm tot} > 1e-3$, indicating that not all the hypotheses are
  poor fits to the transit signal.
\end{itemize}

@@

One final note about these FPP calculations is that unidentified
transit timing variations (TTVs) will increase the FPP of a transit
signal, as the shape of the folded light curve will be distorted,
typically resulting in a longer signal which a trapezoid model will
also identify as more V-shaped.  While we have analyzed light curves
using known TTVs when available, we have also undoubtedly missed many
systems with as-yet-unspecified TTV signals.  This means that a large
FPP may be simply an indication of unidentified TTVs rather than
indicative of an astrophysical false positive, especially in
multi-planet systems, which should overall have a very low false
positive rate.  \Tab{fpp} lists whether known TTVs were accounted for
when constructing the folded transit light curve for each KOI.

@@

In this work, we have calculated the astrophysical false positive
probability (FPP) for every \kepler\ object of interest (KOI), using
the publicly available Python module \vespa.  While the assumptions
behind this calculation are not necessarily valid for every KOI (see
\sect{results:fpp}), we have identified \nvalnew\ KOIs that have
reliable FPPs of $< 0.01$, resulting in validation of their planetary
nature at the 99\% confidence level, more than doubling the
number of confirmed \kepler\ exoplanets.

The reliability of these calculations is dependent largely on the
results of \citet{Bryson:KSCI}, which quantify the probability that
the eclipse/transit signal is spatially coincident on the sky with the
presumed target star.  Without confirmation that the transit signal is
not coming from a significantly displaced source, the sky area used as
part of the prior for the false positive scenarios would need to be
significantly larger than the positional uncertainty value assumed in
this work (described in \sect{methods:fpp}).  Additionally, the
blended false positive scenarios being considered are assumed to be
fully contained within the photometric aperture; this assumption would
also be broken if the source of the eclipse were significantly
displaced.

While previous \emph{a priori} false positive rate estimates
\cite{Morton:2011b,Fressin:2013} have made clear that the
\kepler\ planet candidate catalogs are \emph{generally} low enough to
ignore for the purposes of planet occurrence rate calculations, any
more detailed study of any small subset of individual KOIs must
understand in more detail the FPPs of those specific candidates.  This
type of small-sample candidate culling using individually calculated
FPPs has already been done in the literature
\cite{MortonSwift:2014,MortonWinn:2015}; the publication of this full
catalog allows the community to do the same.

@@

\begin{figure*}[p]
\begin{center}
\includegraphics[width=7in]{figures/fpp_summary_all.pdf}
\end{center}
\caption{False positive probabilities of all CANDIDATE or CONFIRMED
  KOIs for which we consider the \vespa\ calculations to be reliable
  (floored at $10^{-4}$ for visualization purposes), meaning they are
  considered to be reliably located on the target star ($ {\rm Pr} >
  0.99$, with ``score'' $> \posprobthresh$) according to pixel-level analysis
  \citep{Bryson:KSCI}, and have $L_{\rm tot} > 10^{-3}$, indicating
  that the hypotheses tested by \vespa\ are not all poor explanations
  of the data (see \sect{results:fpp}).  Of these \nreliable\ KOIs,
  \nval\ have FPPs less than 1\% (\nvalnew\ of which have not yet been
  dispositioned as CONFIRMED).  Noteably, \nreliableFP\ are likely
  false positives (FPP $> 0.5$), consistent with the
  \citet{Morton:2011b} and \citet{Fressin:2013} \emph{a priori}
  estimates of the overall \kepler\ candidate false positive rate.
  \figlabel{fppall}}
\end{figure*}

\begin{figure*}[p]
\begin{center}
\includegraphics[width=7in]{figures/fpp_pie.pdf}
\end{center}
\caption{A summary of how the the calculations presented in this paper
  advance our understanding of the true nature of KOIs.  More than
  half of all KOIs to date have already been dispositioned FALSE
  POSITIVE or CONFIRMED.  Those dispositioned CANDIDATE we further
  categorize according to their reliability.  The ``no reliable
  calculation'' category means that either the \vespa\ calculation was
  not successful, or that $L_{\rm tot} < 10^{-3}$.  ``On-target
  probability uncertain'' indicates that the positional probability
  calculations of \citet{Bryson:KSCI} are not reliable (score $<
  \posprobthresh$).  ``On-target probability $<$ 0.99'' means that the positional
  probability calculations indicate that there is a non-negligible
  chance that the source of the transit signal is not at the position
  of the KOI.  The remaining three categories are all CANDIDATE KOIs
  reliably confirmed to be located at the presumed target star,
  grouped by false positive probability.  \nvalnew\ of these are new
  planet validations, and \nfpnew\ are new likely false positives.
  \figlabel{fpppie}}
\end{figure*}
